Governing through patronage: the bargain for education in decentralized Brazil

### 2020-10-13 paper/paper.tex

Understanding how these political decisions cascade down the bureaucracy remains a challenge. Public services the end-result of a series of interlocking steps: from personnel decisions to service provision \citep{pepinsky_bureaucracy_2017}, each link in this institutional chain of command connects political principals to the child sitting in the classroom \citep{}.

>>>>

Understanding how these political decisions cascade down the bureaucracy remains a challenge. Public services -- and their quality -- are the end-result of a series of interlocking steps: from personnel decisions to service provision \citep{pepinsky_bureaucracy_2017}, each link in this institutional chain of command connects political principals to the child sitting in the classroom. This panorama of decisions belie a multiplicity of actors that is often obscured in prevailing models of
